Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-15 paper.qmd
Add script to bind the best out of 5 methods

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 190, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  theme(axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7, angle = 90))
```

@@

```{r}
cell_count_scurve <- ggplot(df_bin_centroids_scurve, 
                            aes(x = reorder(as.factor(hexID), 
                                            -std_counts), 
                                y = std_counts)) + 
  geom_quasirandom() + 
  xlab("hexagonal id") + 
  ylab("standardized bin count") +
  geom_hline(yintercept = benchmark1, color = "black", linewidth=0.8, alpha = 0.5) +
  theme(axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, angle = 90),
        axis.text.x = element_text(size = 5, angle = 90),
        axis.text.y = element_text(size = 5))
```

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = benchmark1, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_text(data = benchmark_label_df, 
            aes(x=x, 
                label= label, 
                y=y), 
            colour="black", 
            angle=90) +
  ylab("log(MSE)") +
  xlab("benchmark value") +
  theme(axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, angle = 90))
```

@@

## To draw the distance distribution
distance_scurve$group <- "1"
distance_scurve_plot <- ggplot(distance_scurve, 
                        aes(x = group, 
                            y = distance)) + 
  geom_quasirandom() + 
  ylim(0, max(unlist(distance_scurve$distance))+ 0.5) + 
  coord_flip() + 
  geom_hline(yintercept = benchmark_scurve, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_text(data = benchmark_label_df, 
            aes(x=x, 
                label= label, 
                y=y), 
            colour="black", 
            angle=90) +
  ylab(expression(d^{(2)})) +
  theme(axis.text.x = element_text(size = 5),
        axis.title.x = element_text(size = 5))
```

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 190, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10, angle = 90))
```

@@

```{r}
cell_count_scurve <- ggplot(df_bin_centroids_scurve, 
                            aes(x = reorder(as.factor(hexID), 
                                            -std_counts), 
                                y = std_counts)) + 
  geom_quasirandom() + 
  xlab("hexagonal id") + 
  ylab("standardized bin count") +
  geom_hline(yintercept = benchmark1, color = "black", linewidth=0.8, alpha = 0.5) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10, angle = 90),
        axis.text.x = element_text(size = 7, angle = 90),
        axis.text.y = element_text(size = 10))
```

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = benchmark1, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_text(data = benchmark_label_df, 
            aes(x=x, 
                label= label, 
                y=y), 
            colour="black", 
            angle=90) +
  ylab("log(MSE)") +
  xlab("benchmark value") +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10, angle = 90))
```

@@

## To draw the distance distribution
distance_scurve$group <- "1"
distance_scurve_plot <- ggplot(distance_scurve, 
                        aes(x = group, 
                            y = distance)) + 
  geom_quasirandom() + 
  ylim(0, max(unlist(distance_scurve$distance))+ 0.5) + 
  coord_flip() + 
  geom_hline(yintercept = benchmark_scurve, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_text(data = benchmark_label_df, 
            aes(x=x, 
                label= label, 
                y=y), 
            colour="black", 
            angle=90) +
  ylab(expression(d^{(2)})) +
  theme(axis.text.x = element_text(size = 10),
        axis.title.x = element_text(size = 10))
```
